Wind_analyses

### 2019-03-09 Wind_analyses.Rmd
updated

library(tidyverse)
library(ggpubr)
library(lubridate)
library(stringr)
library(circular)
library(broom)
library(purrr)
library(stlplus)
library(zoo)
source("functions/wind.rose.R")
```

## Wind and wave data obtained from SAWS

@@

#############################################################
#############################################################
This following code is unable to plot the wind patterns (wind roses) as temperature collection occured between 2014-2015 and we do not have wind data that corresponds with these years

@@

wind_daily <- wind_data %>%
  mutate(date = as.Date(date)) %>%
  group_by(site, date) %>%
  summarise(dir_circ = mean.circular(circular(dir, units = "degrees")),
            speed_circ = mean.circular(circular(speed, units = "degrees")))
# save(wind_daily, file = "Data/wind_daily.RData")

@@

temp_wind_MUR <- temp_wind(df = MUR_fyears)
temp_wind_SACTN <- temp_chloro(df = SACTN_fyears)
temp_wind_OISST <- temp_chloro(df = OISST_fyears)
temp_wind_G1SST <- temp_chloro(df = G1SST_fyears)
temp_wind_K10 <- temp_chloro(df = K10_fyears)
```

- Create plots shwoing predominant wind direction during an upwelling evnt
- Create wavelet analyses

>>>>

library(tidyverse)
library(ggpubr)
library(lubridate)
library(stringr)
library(circular)
library(broom)
library(purrr)
library(stlplus)
library(zoo)
source("functions/wind.rose.R")
library(stlplus)
library(forecast)
library(astrochron)
library(WaveletComp)
library(data.table)
# library(plyr)
```

#############################################################
Ignore: run from line 154
#############################################################
## Wind and wave data obtained from SAWS

@@

This following code is unable to plot the wind patterns (wind roses) as temperature collection occured between 2014-2015 and we do not have wind data that corresponds with these years

@@

wind_daily <- wind_data %>%
  mutate(date = as.Date(date)) %>%
  group_by(site, date) %>%
  summarise(dir_circ = mean.circular(circular(dir, units = "degrees")),
            mean_speed = mean(speed))

# save(wind_daily, file = "Data/wind_daily.RData")

@@

temp_wind_MUR <- temp_wind(df = MUR_fyears)
temp_wind_SACTN <- temp_wind(df = SACTN_fyears)
temp_wind_OISST <- temp_wind(df = OISST_fyears)
temp_wind_G1SST <- temp_wind(df = G1SST_fyears)
temp_wind_K10 <- temp_wind(df = K10_fyears)
```

## Visualising the wind data

```{r}

source("functions/wind.rose.R")

renaming_func <- function(df){ 
  renaming <- df %>% 
  dplyr::rename(spd = mean_speed) %>%
  dplyr::rename(dir = dir_circ)
}

temp_wind_MUR <- renaming_func(df = temp_wind_MUR)
temp_wind_SACTN <- renaming_func(df = temp_wind_SACTN)
temp_wind_OISST <- renaming_func(df = temp_wind_OISST)
temp_wind_G1SST <- renaming_func(df = temp_wind_G1SST)
temp_wind_K10 <- renaming_func(df = temp_wind_K10)

## Plotting function

p.wr2 <- plot.windrose(data = temp_wind_SACTN,
              spd = "spd",
              dir = "dir")

p.wr3 <- p.wr2 + facet_wrap(~ site) +
  theme(strip.text.x = element_text(size = 20))
p.wr3
```

# Wavelet analyses

```{r}

library(plyr)

temp_wind_SACTN <-  temp_wind_SACTN %>% 
  drop_na()

temp.d <- function(df){
temp.d <- df %>% 
  dplyr::mutate(no = seq(1:n())) %>%
  dplyr::ungroup() %>% 
  dplyr::select(site, no, dir_circ, date)
}

temp.d <- temp.d(df = temp_wind_SACTN) 
# temp_wind_MUR <- temp_wind(df = MUR_fyears)
# temp_wind_SACTN <- temp_wind(df = SACTN_fyears)
# temp_wind_OISST <- temp_wind(df = OISST_fyears)
# temp_wind_G1SST <- temp_wind(df = G1SST_fyears)
# temp_wind_K10 <- temp_wind(df = K10_fyears)

temp.d <- temp.d %>% 
  select(site, no, dir_circ, date)

prewhite_fun <- function(x) {
  df <- x[, 2:3]
  out <- prewhiteAR(df, order = 3, method = "mle", aic = TRUE,
             genplot = FALSE, verbose = FALSE)
  colnames(out) <- c("no", "dir_circ")
  return(out)
  }
PN_prewhite <- as.tibble(ddply(temp.d, .(site), prewhite_fun))

ggplot(PN_prewhite, aes(x = no, y = dir_circ)) +
  geom_hline(aes(yintercept = mean(dir_circ)), colour = "salmon") +
  geom_line() +
  facet_wrap(~ site, nrow = 4) +
  theme_bw()

wl.fun <- function(x) {
  analyze.wavelet(x, "dir_circ", loess.span = 0, dt = 1,
                   dj = 1/50, lowerPeriod = 2, make.pval = TRUE, n.sim = 50, 
                   method = "white.noise", verbose = FALSE)
}

PN_wave <- dlply(PN_prewhite, .(site), wl.fun)

for (i in 1:length(PN_wave)) {
  attributes(PN_wave[[i]]) <- c(attributes(PN_wave[[i]]), ref = names(PN_wave)[i])
}
# x <- PN_wave[[3]]
plot_fun <- function(x, plot_name = attributes(x)$ref) {
  png(filename = paste0("Figures/new",plot_name,"_wind.png"),
      width = 800, height = 600, units = "px", pointsize = 12, bg = "white")
  wt.image(x, siglvl = 0.05, col.contour = "black", color.key = "quantile",
           timelab = "Days", verbose = FALSE, useRaster = TRUE,
           periodlab = "Period", lwd = 1, graphics.reset = FALSE,
           main = plot_name)
  dev.off()
}
ldply(PN_wave, plot_fun)
```
